---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"BINOMIAL"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to simulate tossing a coin.

* `coin()` creates a coin object (of class `"coin"`)
* `toss()` tosses a coin object, producing a `"toss"` object.
* `plot()` method for a `"toss"` object to plot frequencies of heads.
* `summary()` method for a `"toss"` object.


## Motivation

This package helps the user see functions and methods of the binomial distribution.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
# install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("sp8268/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("sp8268/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)

binvar <- bin_variable(10, 0.5)
summary(binvar)
```
