---
title: "Getting Started with binomial"
author: "Sophie Phillips"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message = F, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", text.align = "center")
library(binomial)
```

##Binomial distribution

This package provides methods and summary statistics for the binomial distribution, a discrete probabilty distribution that models the proability of k successes in n Bernouilli trials with probability p of success.

##Binomial probability

The probability density function of the binomial distribution is given by 

<center> $f(x) = P(x = k) = {n \choose k} p^{k}  (1 - p)^{n - k}$ </center> 

where:

* *n* is the number of (fixed) trials $(n \geq 0)$
* *p* is the probability of success on each trial $(0 \leq p \leq n)$
* 1 - p is the probability of failure on each trial
* *k* is a variable that represents the number of successes out of *n* trials $(0 \leq k \leq n)$
* the first term in parenthesis is NOT a fraction, it is the number of combinations in
which *k* success can occur in *n* trials

{n \choose k} meaning "n choose k" represents the number of possible combinations of k successes in n trials possible. The function bin_choose(n, k) computes this. 
For example, there are 
```{r}
bin_choose(3, 2)
```
ways of getting 2 heads in 5 coin tosses, ie THH, HTH, HHT.

The function bin_probability(success, trials, prob) uses bin_choose to compute the probabilty of *success* successes in *trials* trials with *prob* probability of success. 
For example, the probability of 3 heads in 4 coin tosses using a fair coin (p = 0.5) is 
```{r}
bin_probability(3, 4, 0.5)
```

Requirements:

* *trials* must be a positive integer
* *success* must be a positive integer less than or equal to trials
* *prob* must be a numeric, $0 \leq prob \leq 1$ 

##Binomial Distribution

A distribution is the set of all outcomes with their associated probabilities. To find the distribution of X ~ Bin(trials, prob), use the function bin_distribution(trials, prob).
For example, all possible number of successes in 10 trials with probabilty 0.4 is 
```{r}
bin_distribution(10, 0.4)
```
This output is both a dataframe and bindis object.
Class biindis is plotted as a barplot such as:
```{r}
bindis <- bin_distribution(10, 0.4)
plot(bindis)
```

Requirements:

* *trials* must be a positive integer
* *prob* must be a numeric, $0 \leq prob \leq 1$ 

##Bin cumulative

The cumulative density distribution is also available through the function bin_cumulative(trials, prob)

```{r}
bin_cumulative(10, 0.4)
```
This output is both a dataframe and bincum object.

Class bincum is plotted as a line graph such as:
```{r}
bincum <- bin_cumulative(10, 0.4)
plot(bincum)
```

Requirements:

* *trials* must be a positive integer
* *prob* must be a numeric, $0 \leq prob \leq 1$ 

##Summary Statistics

The summary statistics of a binomial distribution with *trials* and *prob* can be obtained using the following summary functions, all of the format 
bin_<summary statistic>(trials, prob)

* Mean
+ The expected value or mean of a binomial distribution
* Variance
+ Standard deviation squared
* Mode
+ Most likely number of success in given number of trials
* Skewness
+ measure of the asymmetry of the probability distribution of a random variable about its mean
* Kurtosis
+ measure of the “tailedness” of the probability distribution of a random variable.

For example,
```{r}
bin_mean(10, 0.5)
bin_skewness(10, 0.5)
```

##Class Binvar

A binomial variable object stores the values *trials* and *prob*. A binvar object is constructed using the function bin_variable(trials, prob), which returns a binvar object that is stored as a list with named elements trials and prob.
```{r}
binvar <- bin_variable(100, 0.7)
typeof(binvar)
class(binvar)
```

Binvars are printed as
```{r}
x <- bin_variable(100, 0.7)
x
```

You can also obtain summary statistics of the binomial distirbution with the given number of trials and probability using the summary.binvar(binvar) function, which returns a summary.binvar object that is stored as a list with named elements trials, prob, mean, variance, mode, skewness, kurtosis (described in previous section).

##Summary.binvar

A summary binvar object stores the summary statistics of a binomial distribution with binvar's trials and prob of success in a list.

The object is printed with its summary statistics displayed. For example
```{r}
y <- summary(x)
y
```





